
\documentclass[12pt]{amsart}
\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
\geometry{a4paper} % or letter or a5paper or ... etc
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{amsmath}
\usepackage{amsaddr}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{dirtytalk}
\usepackage{float}
\usepackage{listings}
\usepackage{color}
 \title{Exploration of Patterns for use in Class}

\date{\today}

%%% BEGIN DOCUMENT
\begin{document}
\maketitle

\section{Fundamental Patterns}
\section{Definitions}
\begin{enumerate}
	\item Singleton: A set with one value.
	\item Set: A mathematical set. Ex. An undirected graph is a set of edge descriptions.
	\item Sequence: A mathematical sequence. Ex. A digraph is a sequence of edge descriptions.
\end{enumerate}
\section{Functor Pattern}
A  pattern that allows a generic function to apply a specific function  without changing or modifying the generic function.$\\$

\section{Fold Pattern:set or sequence to singleton} 
For function $f$, set or sequence $S$, and singleton $a,\\$

\begin{align*}
 fold(f,S,a) &=
  \begin{cases}
   a & \text{if } S=\varnothing\\
   fold(f,S,f(x:x\in S,a)) & \text{otherwise}
  \end{cases}
\end{align*}
\section{Unfold Pattern:singleton to set or sequence}
For function $f$, and singleton $d\\$
\begin{align*}
unfold(f,d) &=
  \begin{cases}
   \varnothing & \text{if }f(d)=\varnothing\\
   f(d)\cup unfold(f,f(d)) & \text{otherwise}
  \end{cases}
\end{align*}

\section{Derived Patterns}
\subsection{Hylomorphism Pattern}
For functions $f$ and $g$, singleton $d$, and singleton $a,\\$
\begin{align*}
hylo(f,g,d,a) &= fold(f,unfold(g,d),a)
\end{align*}	
\subsection{Map Pattern}
For set or sequence $A=\varnothing$, set or sequence $S$, and function $f$, where $f(s:s\in S, A)$ performs some transformation $t$ as well as $\{t(s)\}\cup A,\\$ 
\begin{align*}
map(f,S) &= fold(f,S,A)
\end{align*}
\subsection{Filter Pattern}
For set or sequence $A=\varnothing$, set or sequence $S$, and function $f$, where $f(s:s\in S, A)$ performs some comparison $c$ and $\{t(s)\}\cup A$ when $c(s)=true,\\$
\begin{align*}
filter(f,S) &= fold(f,S,A)
\end{align*}
\subsection{Monad Pattern}

\subsection{Sream Pattern}
unfold pattern derivative (Stream is the same as Lazy Evaluation)
\end{document}